\documentclass[12pt,letterpaper,notitlepage]{report}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\title{Shell Writeup}
\author{Jordan Taylor and Molli Bishop}



\begin{document}
\maketitle
\begin{quad}
Our decisions were primarily decided on Jordan, who is I, because I wrote the majority of the code in the beginning. It was complicated to fix what was already done. The approach to the decision was to compare the user's input with the commands, and if the input was equivalent to the command then it would call the command. Only until late in the game did I realize that we needed to use fork and execvp even though we had discussed them in class several times. I am pretty ashamed for this and have little to say about it. The difficulties we encountered were of many. Some commands easier than others, the history being the toughest. In fact, I spent several hours trying to get it to work, telling Molli that I could handle it. In a room with James Blakenship, Rikki, and Riley, none of us could seemingly get it to work. Much time was spent on this and it resulted in too much exhaustion to continue and convert the code to use forks. At the start there were many commands that were implemented but they were basic ones. These commands were methods like read and write. One of the additional commands that did get added was help. This function displayed to the user all of the commands, including itself. As for who worked on what, Molli covered the ls, cat, and exit commands whereas I did, and attempted the rest.
\newline
\end{quad}
\end{document}